### 2014-11-12 tex/evaluation.tex
Updated text.

\begin{table} [h]
  \centering
  \begin{tabular}{| c | c | c | c | c | c | c | c |}
  \hline
   \multirow{2}{*}{Method }&\multirow{2}{*}{ $k$ }
   &\multicolumn{2}{|c|}{Time} &\multicolumn{2}{|c|}{ Paths }\\
								&	&\gsetxt{}	&SH	&\gsetxt{} & SH\\
   \hline
    \multirow{3}{*}{LinkedList }&3	& 0.91 & 0.69  &1656 & 25		 \\
   		 				& 4	& 2.92 & 0.91	&17485  & 39 \\
   						& 5	& 20.8 & 1.59 &232743 & 56\\
						& 6	& 283 & 2.36		&3731094 & 76\\
    \hline
    \multirow{3}{*}{BinarySearchTree } & 1	&0.26	& 0.36 & 6	 & 6\\
   		 				& 2	& 0.83 & 0.93	& 143 & 33\\
   						& 3	& 20.6 & 4.03 & 515 & 328\\
    \hline
      \multirow{3}{*}{TreeMap}&1	 & 0.47 & 0.77 &11 & 11 \\
   		 				&2	& 8.99 & 4.72	& 127 & 73 \\
   						& 3	& - & 146	& - & 887 \\

@@

LinkedList
As expected, the repeated use of lazy initialization throughout the program causes an exponential increase in the number of paths explored by \gsetxt{}. By combining many of the \gsetxt{} paths, \shtxt{} avoids the exponential path explosion, demonstrating dramatically reduced, though still exponential, execution time growth. Remarkably, path growth in the k-bound appears to be sub-linear.

In the BinarySearchTree example, the

The TreeMap example has a large number of integer compare instructions, and so it should present the greatest challenge to the constraint solver. However, it still explores far fewer

>>>>

\begin{table} [h]
  \centering
  \begin{tabular}{| c | c | r | r | r | r | }
  \hline
   \multirow{2}{*}{Method }&\multirow{2}{*}{ $k$ }
   &\multicolumn{2}{|c|}{Time} &\multicolumn{2}{|c|}{ Paths }\\
								&	&\gsetxt{}	&SH	&\gsetxt{} & SH\\
   \hline
    \multirow{3}{*}{LinkedList }&3	& 0.91 & 0.69  &1656 & 25		 \\
   		 				& 4	& 2.92 & 0.91	&17485  & 39 \\
   						& 5	& 20.8 & 1.59 &232743 & 56\\
						& 6	& 283 & 2.36		&3731094 & 76\\
    \hline
    \multirow{3}{*}{BinarySearchTree } & 1	&0.26	& 0.36 & 6	 & 6\\
   		 				& 2	& 0.83 & 0.93	& 143 & 33\\
   						& 3	& 20.6 & 4.03 & 515 & 328\\
    \hline
      \multirow{3}{*}{TreeMap}&1	 & 0.47 & 0.77 &11 & 11 \\
   		 				&2	& 8.99 & 4.72	& 127 & 73 \\
   						& 3	& - & 146	& - & 887 \\

@@

As expected, the repeated use of lazy initialization throughout the program causes an exponential increase in the number of paths explored by \gsetxt{}. By combining many of the \gsetxt{} paths, \symtxt{} avoids the exponential path explosion, demonstrating dramatically reduced, though still exponential, execution time growth. Remarkably, path growth in the k-bound appears to be sub-linear.

While the BinarySearchTree example introduces integer constraints, \symtxt{} performance does not appear to suffer due to the constraint burden. Indeed, at k=3, there appears to be a significant performance advantage in favor of \symtxt{}.

The TreeMap example has a large number of integer compare instructions, and so it should present the greatest challenge to the constraint solver. Despite this, \symtxt{} still explores fewer paths than \gsetxt{}, and \gsetxt{} notably failed to terminate within the allotted time bounds for the $k=3$ test case.

### 2014-11-12 tex/related.tex
Updated text.

\subsection{Symbolic Exection}
A number of adaptations to allow symbolic execution to cope with heap data structures have been proposed, beginning with Generalized symbolic execution \cite{GSE03}. Subsequent improvements to the method \cite{Deng:2006,Deng:2007} reduce path explosion by delaying path splitting over aliasing choices for as long as possible. However, since all of the above methods introduce nondeterminism during field reads and writes, they all worsen the path explosion problem to some extent or another. Since our heap representation does not introduce any nondeterminism beyond the level in standard symbolic execution, it will generally create fewer paths than these methods, sometimes by a wide margin.

@@

\subsection{Heap Representations}
A number of other techniques model references using sets of guarded locations \cite{Xie:2005,Cherem:2007,Dillig:2011}. These sets, sometimes known as value sets or value summaries, allow multiple heaps to be represented simultaneously with a higher degree of precision than afforded by shape analysis. However, some of these previous attempts  \cite{Xie:2005,Cherem:2007} utilize non-local recursive definitions for objects. The impact of using recursive definitions for objects is two-fold. First, these techniques must use approximations to resolve reference inequalities, resulting in false positives in the results. Second, these techniques are incapable of reasoning about heaps with loops in the data structures due to infinite recursion during dereferencing. This means that either a large class of data structures must be avoided, or a large class of behaviors must be ignored. In our heap representation, object descriptions are entirely local, thus avoiding these pitfalls. The other work \cite{Dillig:2011}, does not handle structures with loops despite having a local object representation, and has further drawbacks as previously enumerated.

>>>>

\subsection{Symbolic Exection}
As originally formulated, symbolic execution was incapable of reasoning beyond scalar input values. Since then, several adaptations to allow symbolic execution to cope with heap data structures have been proposed, beginning with Generalized symbolic execution \cite{GSE03}. Subsequent improvements to the method \cite{Deng:2006,Deng:2007} reduce path explosion by delaying path splitting over aliasing choices for as long as possible. However, since all of the above methods introduce nondeterminism during field reads and writes, they all contribute to path explosion to some extent. Since our heap representation does not introduce any nondeterminism beyond the level in standard symbolic execution, it will generally create fewer paths than these methods, sometimes by a wide margin.

@@

\subsection{Heap Representations}
One significant line of work on representing heaps is shape analysis. Shape analysis attempts to reduce the complexity of the heap by combining multiple nodes with similar properties into summary nodes. The summary nodes typically establish may/must constraints over the heap structure, and typically represent an overapproximation of the represented heap. As such, program evaluations using shape analysis representations are prone to reporting large numbers of false positives.

As in our representation, other methods have been proposed that model references using sets of guarded locations \cite{Xie:2005,Cherem:2007,Dillig:2011,Sen:2014}. These sets, sometimes known as value sets or value summaries, allow multiple heaps to be represented simultaneously with a higher degree of precision than afforded by shape analysis. However, some of these previous attempts  \cite{Xie:2005,Cherem:2007} utilize non-local recursive definitions for objects. The impact of using recursive definitions for objects is two-fold. First, these techniques must use approximations to resolve reference inequalities, resulting in false positives in the results. Second, these techniques are incapable of reasoning about heaps with recursive data structures due to the potential for infinite recursion during dereferencing. This means that either a large class of data structures must be avoided, or a large class of behaviors must be ignored. In our heap representation, object descriptions are entirely local, thus avoiding these pitfalls. Other methods  \cite{Dillig:2011,Sen:2014}, while having local morphological representations, do not provide for dynamic exploration of the initial heap state.

Another line of work in heap representation lies in identifying isomorphic heap structures in order to avoid exploring redundant paths. Examples of such methods include Korat, XXX, and YYY. These methods are generally focused on the morphology of the heap alone, in isolation from the external constraint problems encountered during program execution. As such, these works are largely orthogonal to the methods presented here, though some of them may possibly be complimentary.
